Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2024-02-17 assets/simulation/power_sx_txrx16.tex
:pencil: Channel singular redistribution

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor2}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor3}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor4}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor5}{rgb}{0.46667,0.67451,0.18824}%
%
\begin{tikzpicture}

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.63413889612284e-05,
ymax=0.000357009156162705,
yminorticks=true,
ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.03593568012931e-05\\
2	8.03593568012931e-05\\
3	8.03593568012931e-05\\
4	8.03593568012931e-05\\
5	8.03593568012931e-05\\
6	8.03593568012931e-05\\
7	8.03593568012931e-05\\
8	8.03593568012931e-05\\
9	8.03593568012931e-05\\
};
\addlegendentry{No RIS}

\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	8.32187269864919e-05\\
2	8.41922087195748e-05\\
3	8.55795092915898e-05\\
4	8.71382957344062e-05\\
5	8.87320958720005e-05\\
};
\addlegendentry{$N_\mathrm{S} = 16$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	8.6466574171426e-05\\
2	8.81326989213474e-05\\
3	9.06190783177407e-05\\
4	9.40273928578491e-05\\
5	9.73131338921825e-05\\
6	9.94886394941543e-05\\
};
\addlegendentry{$N_\mathrm{S} = 32$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	9.23552447351784e-05\\
2	9.66298198027635e-05\\
3	0.000102096862854765\\
4	0.000109010799564887\\
5	0.00011684562278114\\
6	0.000121837810358247\\
7	0.000124553664322635\\
};
\addlegendentry{$N_\mathrm{S} = 64$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.000104965329801996\\
2	0.00011389799786835\\
3	0.000126536878725085\\
4	0.000142525515494825\\
5	0.000160952430585978\\
6	0.000173883585167439\\
7	0.000180725719749113\\
8	0.000184115133386408\\
};
\addlegendentry{$N_\mathrm{S} = 128$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	0.000134020224284578\\
2	0.000153465030738225\\
3	0.000181252804375544\\
4	0.000220639327233136\\
5	0.000268738002904876\\
6	0.000305073448328176\\
7	0.000324412126742617\\
8	0.000334907924545081\\
9	0.000340008720154957\\
};
\addlegendentry{$N_\mathrm{S} = 256$}

\end{axis}
\end{tikzpicture}%

>>>>

% This file was created by matlab2tikz.
%
%The latest updates can be retrieved from
%  http://www.mathworks.com/matlabcentral/fileexchange/22022-matlab2tikz-matlab2tikz
%where you can also make suggestions and rate matlab2tikz.
%
\definecolor{mycolor1}{rgb}{0.85000,0.32500,0.09800}%
\definecolor{mycolor2}{rgb}{0.00000,0.44706,0.74118}%
\definecolor{mycolor3}{rgb}{0.92900,0.69400,0.12500}%
\definecolor{mycolor4}{rgb}{0.49400,0.18400,0.55600}%
\definecolor{mycolor5}{rgb}{0.85098,0.32549,0.09804}%
\definecolor{mycolor6}{rgb}{0.46600,0.67400,0.18800}%
\definecolor{mycolor7}{rgb}{0.30100,0.74500,0.93300}%
\definecolor{mycolor8}{rgb}{0.92941,0.69412,0.12549}%
\definecolor{mycolor9}{rgb}{0.63500,0.07800,0.18400}%
\definecolor{mycolor10}{rgb}{0.00000,0.44700,0.74100}%
\definecolor{mycolor11}{rgb}{0.49412,0.18431,0.55686}%
\definecolor{mycolor12}{rgb}{0.46667,0.67451,0.18824}%
\definecolor{mycolor13}{rgb}{0.50196,0.50196,0.50196}%
%
\begin{tikzpicture}

\begin{axis}[%
width=7.607cm,
height=6cm,
at={(0cm,0cm)},
scale only axis,
xmin=1,
xmax=9,
xtick={1,2,3,4,5,6,7,8,9},
xticklabels={{$2^0$},{$2^1$},{$2^2$},{$2^3$},{$2^4$},{$2^5$},{$2^6$},{$2^7$},{$2^8$}},
xlabel style={font=\color{white!15!black}},
xlabel={RIS Group Size},
ymode=log,
ymin=7.71952537202106e-05,
ymax=0.000358145391898644,
yminorticks=true,
ylabel style={font=\color{white!15!black}},
ylabel={Channel Power [W]},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
yminorgrids,
legend style={at={(0.03,0.97)}, anchor=north west, legend cell align=left, align=left, draw=white!15!black}
]
\addplot [color=black, line width=2.0pt]
  table[row sep=crcr]{%
1	8.12581618107481e-05\\
2	8.12581618107481e-05\\
3	8.12581618107481e-05\\
4	8.12581618107481e-05\\
5	8.12581618107481e-05\\
6	8.12581618107481e-05\\
7	8.12581618107481e-05\\
8	8.12581618107481e-05\\
9	8.12581618107481e-05\\
};
\addlegendentry{No RIS}

\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.74153313091917e-05\\
};
\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor2, forget plot] table[row sep=crcr]{%
x	y\\
5	8.74291033971713e-05\\
};
\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor5, forget plot] table[row sep=crcr]{%
x	y\\
6	9.91843205545709e-05\\
};
\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor5, forget plot] table[row sep=crcr]{%
x	y\\
6	9.91780210311253e-05\\
};
\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
7	0.00012405412223482\\
};
\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor8, forget plot] table[row sep=crcr]{%
x	y\\
7	0.000124044149009442\\
};
\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor11, forget plot] table[row sep=crcr]{%
x	y\\
8	0.000182844868229739\\
};
\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor11, forget plot] table[row sep=crcr]{%
x	y\\
8	0.000182852647982853\\
};
\addplot[only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor12, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000339584399340245\\
};
\addplot[only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor12, forget plot] table[row sep=crcr]{%
x	y\\
9	0.000339587956470715\\
};

\addplot[draw=none, only marks, mark=triangle, mark options={rotate=90}, mark size=2pt, line width=2pt, draw=mycolor13] table[row sep=crcr]{%
x	y\\
1	1\\
};
\addlegendentry{OP-left}

\addplot[draw=none, only marks, mark=triangle, mark options={rotate=270}, mark size=2pt, line width=2pt, draw=mycolor13] table[row sep=crcr]{%
x	y\\
1	1\\
};
\addlegendentry{OP-right}

\addplot [color=mycolor2, line width=2.0pt]
  table[row sep=crcr]{%
1	8.41788427928869e-05\\
2	8.50641788557691e-05\\
3	8.63696852707132e-05\\
4	8.79903454326538e-05\\
5	8.96339735645668e-05\\
};
\addlegendentry{$N_\mathrm{S} = 16$}

\addplot [color=mycolor5, dashed, line width=2.0pt]
  table[row sep=crcr]{%
1	8.72783634122255e-05\\
2	8.91184079692796e-05\\
3	9.17640563659579e-05\\
4	9.50977289249081e-05\\
5	9.85503564245316e-05\\
6	0.00010076742152366\\
};
\addlegendentry{$N_\mathrm{S} = 32$}

\addplot [color=mycolor8, dotted, line width=2.0pt]
  table[row sep=crcr]{%
1	9.36120443845964e-05\\
2	9.75056089045287e-05\\
3	0.000102998044584118\\
4	0.000110120638452998\\
5	0.0001177772588008\\
6	0.000122854470762259\\
7	0.000125497666976946\\
};
\addlegendentry{$N_\mathrm{S} = 64$}

\addplot [color=mycolor11, dashdotted, line width=2.0pt]
  table[row sep=crcr]{%
1	0.000106289915229579\\
2	0.000114680256721358\\
3	0.000126826397397359\\
4	0.000142994695102657\\
5	0.00016107230730003\\
6	0.000173889895707073\\
7	0.000180752926606848\\
8	0.000184267352458571\\
};
\addlegendentry{$N_\mathrm{S} = 128$}

\addplot [color=mycolor12, line width=2.0pt]
  table[row sep=crcr]{%
1	0.000134334856638143\\
2	0.000153364621257308\\
3	0.000182125698990213\\
4	0.000221951821498391\\
5	0.000269865717893532\\
6	0.000305861046930524\\
7	0.00032571637890533\\
8	0.000335868097136638\\
9	0.00034109084942728\\
};
\addlegendentry{$N_\mathrm{S} = 256$}

\end{axis}

\begin{axis}[%
width=9.816cm,
height=7.362cm,
at={(-1.276cm,-0.81cm)},
scale only axis,
xmin=0,
xmax=1,
ymin=0,
ymax=1,
axis line style={draw=none},
ticks=none,
axis x line*=bottom,
axis y line*=left
]
\end{axis}
\end{tikzpicture}%

### 2024-02-17 main.tex
:pencil: Channel singular redistribution

	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\%, 312\%, 537\% over single-connected in $1 \times 1$, $4 \times 4$, $16 \times 16$ \gls{mimo} under independent Rayleigh fading, respectively.
	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			% The observations align with Proposition \ref{pp:rank_deficient} that t
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
					\resizebox{0.4725\columnwidth}{!}{
						\input{assets/simulation/power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
					\resizebox{0.4875\columnwidth}{!}{
						\input{assets/simulation/power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
				}
				\label{fg:power_bond}
			\end{figure}

@@

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
				\resizebox{0.49\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx4_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:power_sx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
				\resizebox{0.49\columnwidth}{!}{
					\input{assets/simulation/rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/rate_txrx.tex}
				}
			}
			\\
			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/rate_sx.tex}
				}
			}
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/rate_kfactor.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:rate}
		\end{figure}
	\end{subsection}
	% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);

>>>>

	Fourth, extensive simulations reveal that the performance gain from \gls{bd}-\gls{ris} increases with group size and \gls{mimo} dimensions.
	In terms of channel power, fully-connected \gls{bd}-\gls{ris} boosts up to 62\% and 270\% over diagonal \gls{ris} in $1 \times 1$ and $4 \times 4$ \gls{mimo} under independent Rayleigh fading, respectively.
	The superiority stems from stronger \emph{subchannel rearrangement} and \emph{subspace alignment} capabilities empowered by in-group cooperation.
	It emphasizes the importance of using \gls{bd}-\gls{ris} in large-scale \gls{mimo} systems.

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			% The observations align with Proposition \ref{pp:rank_deficient} that t
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
					\resizebox{!}{3.25cm}{
						\input{assets/simulation/power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
				}
				\label{fg:power_bond}
			\end{figure}

@@

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/power_sx_txrx4_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:power_sx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_beamforming}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/rate_beamforming.tex}
				}
			}
			\subfloat[$N_\mathrm{T} \times 128 \times N_\mathrm{R}$\label{fg:rate_txrx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/rate_txrx.tex}
				}
			}
			\\
			\subfloat[$4 \times N_\mathrm{S} \times 4$\label{fg:rate_sx}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/rate_sx.tex}
				}
			}
			\subfloat[$4 \times 128 \times 4$\label{fg:rate_kfactor}]{
				\resizebox{!}{3.25cm}{
					\input{assets/simulation/rate_kfactor.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:rate}
		\end{figure}
	\end{subsection}
	% [channel.pathloss.distance.direct, channel.pathloss.distance.forward, channel.pathloss.distance.backward, channel.pathloss.exponent.direct, channel.pathloss.exponent.forward, channel.pathloss.exponent.backward] = deal(-14.7, -10, -6.3, -3, -2.4, -2);
